Sparse Representation Approaches for First Stage Retrieval: A Review

### 2022-01-06 src/article.tex
Add training paragraph for SparTerm.

>>>>

    \paragraph{Training.}
    BERT (12-layer, 768-hidden, 12-heads, 110M parameters) is used for the Gating Controller
    and Importance Predictor.
    They are initialized with pre-trained models.
    First, the Gating Controller is fine-tuned for 50k iterations where
    $\lambda_1 = 1e - 3$ and $\lambda_2 = 1$.
    Then Gating Controller parameters are fixed and SparTerm model is fine-tuned jointly for 100k
    iterations.
    Adam optimizer is selected with the learning rate $2 \cdot 10^{-5}$.\\\par
